Whitepaper: Contract Modules

### 2020-12-03 meeting-notes/20201108-expose-input-language.tex

The current Tezos API facing to OCaml (as well as the one provided by
the Tezos client) is untyped. Here we propose a DSL to make it typed.
First we recall some information from the Michelson white paper
\url{https://tezos.gitlab.io/whitedoc/michelson.html#core-data-types-and-notations}.

@@

tlserializer = s_or s_bool (s_option s_string) :
               [`Left of bool | `Right of string option] -> string
\end{lstlisting}
\end{document}

>>>>

The current Tezos API for invoking contracts with parameters is
untyped. This manifests in the input of the Tezos client where
parameters have to be supplied as strings and are then parsed before
they are passed to the contract execution. For example:
\begin{lstlisting}[language=sh]
tezos-client transfer 10000 from contractOwner to v1-public-pool 
--arg '(Left Unit)' --burn-cap 0.004
\end{lstlisting}
This is also true for the first cut of the OCaml API.

 Here we propose a DSL to make it typed.
First we recall some information from the Michelson white paper
\url{https://tezos.gitlab.io/whitedoc/michelson.html#core-data-types-and-notations}.

@@

tlserializer = s_or s_bool (s_option s_string) :
               [`Left of bool | `Right of string option] -> string
\end{lstlisting}

Query the Tezos blockchain for the type of a contract and its
entrypoints.
\begin{lstlisting}[language=Caml]
make_typed_contract : contract_hash -> 't Mtype -> 't Contract
\end{lstlisting}
The function call \lstinline/make_typed_contract hash mty/ would query
the node (via client lib or rpc) for the type of the contract
\lstinline/hash/ and check it against \lstinline/mty/.
This call fails if the type \lstinline/mty/ does not match the
stored type of the contract.
The returned value contains the serializer from \lstinline/'t -> string/.
\begin{lstlisting}[language=Caml]
invoke_typed : 't Contract -> 't -> result Tezos.apimonad
\end{lstlisting}
\end{document}

### 2020-12-03 papers/contract-modules/modules.tex

\lstdefinelanguage{michelson}{
  % basicstyle=\ttfamily{},
  classoffset=0,
  morekeywords={parameter,storage,code},
  keywordstyle=\bfseries, 
  % predefined types
  classoffset=1,
  morekeywords={nat,int,unit,string,union,pair,option,address},
  keywordstyle=\color{blue},
  classoffset=2,
  morekeywords={CAR,CDR,CONS,DUP,EQ,FAILWITH,IF,IF_LEFT,LE,LEFT,NIL,POP,PUSH,RIGHT,SENDER,SUB},
  keywordstyle=\color{magenta},
  backgroundcolor=\color{pink!20}
}

@@

Consider this Michelson code fragment:
\begin{lstlisting}[language=michelson,caption={Michelson code example},label={lst:code-example}]
parameter (union (int %bid_for_auction)
                 (unit %close_auction));
storage address;
code { DUP; CAR; 
       IF_LEFT {
       # %bid_for_auction
        DUP; PUSH int 10000; SUB; LE;
        IF { FAILWITH; } {} # fails with argument value
        # ...
        { PUSH string "closed"; FAILWITH; }
        # ...
        { PUSH string "bid too low"; FAILWITH; }
        # ...
        { PUSH int 42; FAILWITH; }
        # ...
       }
       {
       # %close_auction
         POP; CDR; SENDER; EQ;
         IF {} { PUSH string "not owner"; FAILWITH; }
         # ...
       }
     }
\end{lstlisting}

>>>>

\lstdefinelanguage{michelson}{
  % basicstyle=\ttfamily{},
  classoffset=0,
  morekeywords={parameter,storage,code},
  keywordstyle=\bfseries, 
  % predefined types
  classoffset=1,
  morekeywords={nat,int,unit,string,or,pair,option,address},
  keywordstyle=\color{blue},
  classoffset=2,
  morekeywords={CAR,CDR,CONS,DUP,EQ,FAILWITH,IF,IF_LEFT,LE,LEFT,NIL,DROP,PUSH,RIGHT,SENDER,SUB},
  keywordstyle=\color{magenta},
  backgroundcolor=\color{pink!20}
}

@@

Consider this Michelson code fragment:
\begin{lstlisting}[language=michelson,caption={Michelson code example},label={lst:code-example}]
parameter (or (int %bid_for_auction)
              (unit %close_auction));
storage address;
code { DUP; CAR; 
       IF_LEFT {
       # %bid_for_auction
        DUP; PUSH int 10000; SUB; LE;
        IF { FAILWITH; } {} # fails with argument value
        # ...
        { PUSH string "closed"; FAILWITH; }
        # ...
        { PUSH string "bid too low"; FAILWITH; }
        # ...
        { PUSH int 42; FAILWITH; }
        # ...
       }
       {
       # %close_auction
         DROP; CDR; SENDER; EQ;
         IF {} { PUSH string "not owner"; FAILWITH; }
         # ...
       }
     }
\end{lstlisting}
